### 2024-08-10 paper.tex
dimension of centralizer

>>>>

The dimension of \(u'_{ij}\) is \(\min(\lambda_i, \lambda_j)\) in the case that \(i \neq i_0\), and \(\min(\lambda_i - j_0, \lambda_j)\) when \(i = i_0\).
Write \(d_{ij}\) for this dimension.
For each \(i\), let \(q_i\) be the length of the longest prefix of \(b_i\) which consists of zeroes.
\par Fix an \(i\).
I claim the rank of the matrix of \(b\)'s is \(h := \max_j [d_{ij} - q_j]\), or zero if this quantity is always negative.
First, to see that the rank is at least this big, note that for any \(j \in \argmax_j [d_{ij} - q_j]\), the rank of the \(j\)th ``column block'' of the matrix of \(b\)'s is equal to \(h\).
Then, to see that the rank is at most this big, note that every row after the first \(h\) rows is just zeroes.
So, the total degrees of freedom for the \(u_{ij}\) is 
\[\sum_j d_{ij} - \max(0, \max_j [d_{ij} - q_j]).\]
Then summing over all the \(i\), we get the dimension of \(C_3\):
\[\sum_i \sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j]).\]
